Binary companions of red clump stars

### 2017-03-05 paper/main.tex
intro: why RC stars

% to-do list
% ----------
% -

@@

HOGG: Why are \RC\ or \RGB\ stars ideal candidates? It has to do with the
unlikelihood that they will be SB2. Also: abundances! Also: masses!
Also: distances! and so on.!

@@

>>>>

% to-do list
% ----------
% - write a first draft of the introduction
% - list our assumptions for detection & characterization (TheJoker)
% - list our assumptions for hierarchical inference

@@

For the study of single-line binaries, red-giant stars---and even
better red-clump stars---are ideal.
For one, because they are so luminous, they are unlikely (in general)
to have equally-bright companions, and therefore are well approximated
or fit as single-line objects.
For two, they are standard candles, or can be distance-calibrated.
For three, they have masses that can be estimated spectrally (making
use of dredged-up elements; CITE MARTIG and CITE NESS).
With primary-star mass estimates, the binary-orbit fitting will return
$m\,\sin i$ estimates for the secondary, and not just mass-function
estimates.
For four, the \apogee\ pipelines, and also \thecannon\, produce
detailed abundance estimates for red giants and \RC\ stars.
If there are causal relationships between chemical abundances and
binary companions---and we expect there will be---these should become
visible here.

@@

\section{Method: Detection and orbit fitting}

\section{A catalog of red-clump binary systems}

\section{Method: Population inferences}

\section{The population of red-clump binary companions}

\section{Discussion}
